% LaTeX Curriculum Vitae Template
% Based on Jason Blevins' CV template
% Adapted for automated generation from JSON data

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}

% Use Palatino font for a professional look
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Woohun Son}

% Set footer link
\def\footerlink{https://SonWoohun.github.io}

% PDF metadata
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {economics, research, academic},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

% Page geometry
\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Don't indent paragraphs
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

\vspace{0.25in}

\begin{minipage}{0.45\linewidth}
  The Ohio State University \\
  Ph.D in Economics \\
  Columbus, Ohio
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Email: & \href{mailto:son.268@osu.edu}{\tt son.268@osu.edu} \\
    Homepage: & \href{https://SonWoohun.github.io}{\tt https://SonWoohun.github.io} \\
    GitHub: & \href{https://github.com/SonWoohun}{\tt https://github.com/SonWoohun} \\
  \end{tabular}
\end{minipage}


\section*{Education}

\begin{itemize}
  \item Ph.D in Economics, The Ohio State University, 2028 (expected).
  \item M.A. in Economics, The Ohio State University, 2023.
  \item M.A. in Economics, Korea University, 2022.
  \item B.A. in Korean history and Economics (double major), Korea University, 2019.
\end{itemize}


\section*{Employment}

\begin{itemize}
\item Graduate Research Assistant, The Ohio State University, 2025-05-06--2025-08-15.
\item Graduate Research Assistant, NYU Abu Dhabi, 2021-10-01--2022-06-30.
\end{itemize}


\section*{Teaching}

\begin{itemize}
\item Teaching Assistant, Undergraduate Theory of Taxation, Spring 2021.
\item Teaching Fellow, Undergraduate Principles of Economics 1, Spring 2020, Spring 2021.
\item Teaching Assistant, Undergraduate Econometrics 1, Fall 2019, Spring 2020, Fall 2020.
\end{itemize}


\section*{Languages}

\begin{itemize}
\item Korean (Korean (Native)).
\item English (English (Fluent)).
\end{itemize}


\bigskip

% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    \href{\footerlink}{\texttt{\footerlink}}
  \end{footnotesize}
\end{center}

\end{document}
